ms_tables

### 2018-11-14 man/ms_tables/t_robust_anovas.Rmd
update tables

---
output:  
  word_document:
    reference_docx: "../../man/template_tables_portrait.docx"
---

@@

dff_evi <- evi %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drougth event", 
                           "disturb_year:site" = "Drougth event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drougth event", "Site", "Drougth event X Site"))) %>% 
  mutate_at(c(2,4,6,8), round, 2) %>% 
  mutate_at(c(3,5,7,9), round, 3) %>% 
  mutate(variable = 'evi')

@@

dff_bai <- bai %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drougth event", 
                           "disturb_year:site" = "Drougth event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drougth event", "Site", "Drougth event X Site"))) %>% 
  mutate_at(c(2,4,6,8), round, 2) %>% 
  mutate_at(c(3,5,7,9), round, 3) %>% 
  mutate(variable = 'bai')

@@

```{r, echo=FALSE}
colnames(dff) <- c("variable", "factores", "rt\nF", "rt\np", "rc\nF", "rc\np", "rs\nF", "rs\np")
pander(dff)
```

>>>>

---
output:  
  pdf_document
---

@@

dff_evi <- evi %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drought event", 
                           "disturb_year:site" = "Drought event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drought event", "Site", "Drought event X Site"))) %>% 
  mutate_at(c(2,4,6,8), round, 2) %>% 
  mutate_at(c(3,5,7,9), round, 3) %>% 
  mutate(variable = 'evi')

@@

dff_bai <- bai %>% gather(temp, numeros, F, p) %>% 
  unite(temp1, variables, temp) %>% 
  spread(temp1, numeros) %>% 
  mutate(factores = recode(factores, 
                           "disturb_year" = "Drought event", 
                           "disturb_year:site" = "Drought event X Site", 
                           "site" = "Site")) %>% 
  arrange(match(factores, c("Drought event", "Site", "Drought event X Site"))) %>% 
  mutate_at(c(2,4,6,8), round, 2) %>% 
  mutate_at(c(3,5,7,9), round, 3) %>% 
  mutate(variable = 'bai')

@@

```{r, echo=FALSE}
# https://haozhu233.github.io/kableExtra/use_kableExtra_with_formattable.html
colnames(dff) <- c("variable", "factors", "F", "p", "F", "p", "F", "p")
kable(dff, format = "latex") %>% add_header_above(c("", "", "Resistance" = 2, "Recovery" = 2, "Resilience" = 2))

# https://davidgohel.github.io/flextable/articles/examples.html

```
